Energy and the CES production function

### 2015-08-21 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
model_points --> model_points_style

<<model_points>>=
model_points <- function(p) {
  p + 
  scale_colour_manual(values = c("gray70", "black")) +
  scale_size_manual(values = c(5, 3,3,3,3,3,3)) +
  # scale_alpha_manual(values = c(.2, .6,.6,.6,.6, .6, .6)) +
  scale_fill_manual(values = c(scales::alpha("gray50", .2), rep("transparent", 6))) +
  scale_shape_manual(values = c(21, 21, 23:27)) +
  guides( 
    col = guide_legend(override.aes = aes(size = 5, shape = 21)) )
}

@@

model_points(p)
@

@@

p <- triPlot(
  data=
    AllCoeffs %>% filter(model == "CES") %>%
    mutate( Model = interaction(nest, CSP, sep = " ", drop=TRUE),
            Inputs = flavor), 
  grid_lines = 5,
  labels = c("alpha[k]", "alpha[l]", "alpha[e]"),
  aes(x = alpha_1, y = alpha_2, z = alpha_3, 
      fill  = Model, 
      shape = Model,
      size = Model,
      color = Inputs)
  ) +
  facet_grid(. ~ Country)
  model_points(p)
@

>>>>

<<model_points>>=
model_points_style <- function(p) {
  p + 
  scale_colour_manual(values = c("gray70", "black")) +
  scale_size_manual(values = c(5, 3,3,3,3,3,3)) +
  # scale_alpha_manual(values = c(.2, .6,.6,.6,.6, .6, .6)) +
  scale_fill_manual(values = c(scales::alpha("gray50", .2), rep("transparent", 6))) +
  scale_shape_manual(values = c(21, 21, 23:27)) +
  guides( 
    col = guide_legend(override.aes = aes(size = 5, shape = 21)) )
}

@@

model_points_style(p)
@

@@

p <- triPlot(
  data=
    AllCoeffs %>% filter(model == "CES") %>%
    mutate( Model = interaction(nest, CSP, sep = " ", drop=TRUE),
            Inputs = flavor), 
  grid_lines = 5,
  labels = c("alpha[k]", "alpha[l]", "alpha[e]"),
  aes(x = alpha_1, y = alpha_2, z = alpha_3, 
      fill  = Model, 
      shape = Model,
      size = Model,
      color = Inputs)
  ) +
  facet_grid(. ~ Country)
  model_points_style(p)
@
